Modeling Soot in Oxy-Coal Combustion Systems using Large Eddy Simulations

### 2019-11-20 manuscript/manuscript.tex
adding .gitignore, making manuscript.tex use elsarticle.cls

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[12pt]{wssci}

@@

\usepackage{biblatex}
\addbibresource{references.bib}
%======================================================================
\newcommand\papertopic{Turbulent Flames}
\newcommand\tprime{\prime\prime\prime}
%======================================================================

@@

\author[1]{Kamron Brinkerhoff}
\author[1]{Alex Josephson}
\author[2]{Ben Isaac}
\author[2]{Jeremy Thornock}
\author[1]{Andrew Fry}
\author[1,*]{David Lignell}

\affil[1]{Department of Chemical Engineering, Brigham Young University, Provo, UT, 84602, United States}
\affil[2]{Department of Chemical Engineering, University of Utah, Salt Lake City, UT 84112, United States}
\affil[*]{Corresponding author: \email{davidlignell@byu.edu}}

\begin{document}
\maketitle

@@

@@

\printbibliography

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass[review,3p]{elsarticle}
%\documentclass[5p]{elsarticle}

@@

\usepackage{biblatex}
\addbibresource{references.bib}
%======================================================================
\newcommand\tprime{\prime\prime\prime}
\newcommand{\prtl}[2]{\frac{\partial #1}{\partial #2}}
%======================================================================

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%\preprint{}

@@

\author[byu]{Kamron Brinkerhoff}
\author[lanl]{Alex Josephson}
\author[llnl]{Ben Isaac}
\author[uofu]{Jeremy Thornock}
\author[byu]{Andrew Fry}
\author[byu,*]{David Lignell\corref{cor1}}
\ead{davidlignell@byu.edu}

\address[byu]{350 CB, Brigham Young University, Provo, UT 84602, USA}
\address[lanl]{350 CB, Brigham Young University, Provo, UT 84602, USA}
\address[llnl]{350 CB, Brigham Young University, Provo, UT 84602, USA}
\address[uofu]{350 CB, Brigham Young University, Provo, UT 84602, USA}
\cortext[cor1]{Corresponding author}

\journal{Combustion and Flame}

\date{\today}

@@

\maketitle

\linenumbers

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\bibliographystyle{elsarticle-num}
\bibliography{references}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
